---
title: "hybrid_app"
output: html_document
runtime: shiny
resource_files:
- app.R
- CGM_data.rda
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This R Markdown document is made interactive using Shiny. Unlike the more traditional workflow of creating static reports, you can now create documents that allow your readers to change the assumptions underlying your analysis and see the results immediately. 

To learn more, see [Interactive Documents](http://rmarkdown.rstudio.com/authoring_shiny.html).

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r eruptions, echo=FALSE}

load("CGM_data.rda")
library(shiny)
library(shinydashboard)
library(leaflet)
library(dplyr)
library(curl) # make the jsonlite suggested dependency explicit
library(dygraphs)
library(dashboardthemes)
library(shinythemes)
library(xts)
library(plyr)
library(sf)

# UI

ui <- fluidPage(
    
    # Application title
    theme = shinythemes::shinytheme("yeti"),
    titlePanel(h1("OxAir - Hybrid AQ Data Map", align = "center")),
    
    dashboardBody(
        fluidRow(
            column(width = 12,
                   box(width = NULL, status = "warning", align = "center",
                       uiOutput("routeSelect"),
                       p(
                           class = "text-muted",
                           paste("Note: each 'Journey' represents a different OxAir Competency Group member's path through Oxford. Data was collected at different dates and times."
                           )
                       ),
                       selectInput(inputId = "Selector",
                                   label = "Select Example Journey",
                                   choices = c("Please Select:",
                                               "CGM1",
                                               "CGM2"),
                                   selected = "Please Select:"),
                   ),
            ),
            column(width = 6,
                   box(width = NULL, solidHeader = TRUE, style='padding:10px;',
                       leafletOutput(outputId = "oxmap", height = 400), 
                   )),
            column(width = 6,
                   box(width = NULL, height = 300, style='padding:10px;',
                       dygraphOutput("CGM1_pm2_5_timeseries")
                   )),
        ),
    ))


# SERVER
server <- function(input, output) {
    
    output$oxmap <- renderLeaflet({
        
        icons <- awesomeIcons(
            icon = 'bicycle',
            markerColor = 'white',
            library = 'ion'
        )
        
        pal <- colorFactor(palette = 'RdYlGn',domain = b$pm2_5)
        
        map <- leaflet(b) %>% 
            addProviderTiles(providers$CartoDB.DarkMatter) %>% 
            addCircleMarkers(color= ~pal(pm2_5),opacity = 0.5, radius = 2) %>% 
            addAwesomeMarkers( #markers need to change location & content according to each CG_member
                lng = -1.265375, lat = 51.77881,
                icon=icons,
                label = "TEST 1",
                labelOptions = labelOptions(noHide = F)) %>%
            addAwesomeMarkers(
                lng = -1.266362, lat = 51.77441,
                icon=icons,
                label = "TEST 2",
                labelOptions = labelOptions(noHide = F))
            
        map
        
    })
    
    #leaflet polylines & dygraph widgets should be connected so that when you hover over dygraph, location of reading shows up as a circle on leaflet map
    
    output$CGM1_pm2_5_timeseries <- renderDygraph({ #dygraph should change when specific CG_member is selected from dropdown menu, also include tabs for PM and NO2
        xts(x = master_df_pm$pm2_5, order.by = master_df_pm$datetime) %>%
            dygraph() %>%
            dyOptions(drawPoints = TRUE, pointSize = 4) %>%
            dyLimit(0, "Low", labelLoc="right", color="grey") %>%
            dyLimit(30, "Medium", labelLoc="right", color="grey") %>%
            dyLimit(70, "High", 
                    labelLoc="right", color="grey") %>%
            dyLimit(500, "Very High", labelLoc="right", color="grey") %>%    
            dyShading(0, 29, color="#ccff99", axis="y") %>%
            dyShading(30, 69, color="#ffffcc", axis="y") %>%
            dyShading(70, 499, color="#ffebcc", axis="y") %>%
            dyShading(500, 1000, color="#ffcccc", axis="y") %>%
            dyOptions(colors = RColorBrewer::brewer.pal(3, "Set1")) %>%
            dyLegend(width = 200, show = "follow") %>%
            dyRangeSelector(height = 20) 
    })
}

rsconnect::deployApp("shinyapps/oxair_hybrid_map/hybrid_app.rmd", account = 'kayla-schulte')

```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



